Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2023-09-14 manuscript.qmd
Minor edit

# create python environment and install packages
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}
use_virtualenv('env/')

>>>>

# create python environment and install packages
if (processedata==2){
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}
use_virtualenv('env/')
}
